---
title: "ASSR_2ndharm"
author: "Stefan Wiens & Malina Szychowska"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes

---
<style>
body {text-align: justify}
</style>

```{r setup, include = FALSE}
#'echo = False' hides *all* code chunks below when knitted 
#'warning = F' hides *all* warnings messages below when knitted 
#'message = F' hides *all* messages below when knitted 

knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
knitr::opts_chunk$set(fig.width=12, fig.asp=0.6, fig.align="center")
```

```{r prepare R, echo = FALSE, include = FALSE}
# clear memory and set random seed
rm(list = ls()) # clear memory
graphics.off()  # clear all plots
cat("\014")     # clear console (same as Ctrl-L in console)
set.seed(123)   # Makes it reproducable also if random number generators are used

# set up working directory
experiment = 'ASSR2'

## Stefan
#dir_main = file.path('C:','Users',Sys.getenv("USERNAME"),'Documents','Box Sync',experiment)

# Malina
dir_main = file.path('C:','Users',Sys.getenv("USERNAME"),'Box Sync','Malina_dissertation', 'additional analyses for the defense', '20Hz second harm')

# knit in R directory
knitr::opts_knit$set(file.path(dir_main,'R_scripts'))

source('ASSR_2ndharm_set_up.r')

# save output data files to result directory
dir_res = file.path(dir_main,'results')

# save figures to an extra directory
dir_fig = file.path(dir_res, 'figures')

# define if extra output should be printed
rout = TRUE

# change to working directory (not necessary)
# setwd(file.path(dir_main,'R_scripts'))
```

```{r read in audio EEG data, echo = rout}
DSIV_s1=read.csv(file.path(dir_res, paste0("data_audio_signal_noise_ASSR_study1_2nd_harmonic.tsv")), sep="\t",header=TRUE, dec=".")
DSIV_s2=read.csv(file.path(dir_res, paste0("data_audio_signal_noise_ASSR_study2_2nd_harmonic.tsv")), sep="\t",header=TRUE, dec=".")
DSV=read.csv(file.path(dir_res, paste0("data_audio_signal_noise_ASSR2_2nd_harmonic.tsv")), sep="\t",header=TRUE, dec=".")
```

```{r check for unique subject numbers, echo = rout}
if (any(as.numeric(table(DSIV_s1$fp))!=1)){
  stop("Subject numbers are not unique!")
}

if (any(as.numeric(table(DSIV_s2$fp))!=1)){
  stop("Subject numbers are not unique!")
}

if (any(as.numeric(table(DSV$fp))!=1)){
  stop("Subject numbers are not unique!")
  }
```

```{r create EEG amp variables, echo = rout}
# Amp S-N raw

# ASSR Study 1
# the numbers 1 to 4 refer to different blocks

DSIV_s1$AmpSmNlo = rowMeans(cbind(DSIV_s1$AmpSmNlo1,DSIV_s1$AmpSmNlo2,DSIV_s1$AmpSmNlo3,DSIV_s1$AmpSmNlo4))
DSIV_s1$AmpSmNhi = rowMeans(cbind(DSIV_s1$AmpSmNhi1,DSIV_s1$AmpSmNhi2,DSIV_s1$AmpSmNhi3,DSIV_s1$AmpSmNhi4))

# ASSR Study 2
# the numbers 1 to 4 refer to different blocks
DSIV_s2$AmpSmNno = rowMeans(cbind(DSIV_s2$AmpSmNno1,DSIV_s2$AmpSmNno2,DSIV_s2$AmpSmNno3,DSIV_s2$AmpSmNno4))
DSIV_s2$AmpSmNlo = rowMeans(cbind(DSIV_s2$AmpSmNlo1,DSIV_s2$AmpSmNlo2,DSIV_s2$AmpSmNlo3,DSIV_s2$AmpSmNlo4))
DSIV_s2$AmpSmNhi = rowMeans(cbind(DSIV_s2$AmpSmNhi1,DSIV_s2$AmpSmNhi2,DSIV_s2$AmpSmNhi3,DSIV_s2$AmpSmNhi4))
DSIV_s2$AmpSmNvh = rowMeans(cbind(DSIV_s2$AmpSmNvh1,DSIV_s2$AmpSmNvh2,DSIV_s2$AmpSmNvh3,DSIV_s2$AmpSmNvh4))

# ASSR2
# the numbers 1 to 2 refer to different blocks
DSV$AmpSmNno20Hz = rowMeans(cbind(DSV$AmpSmNno20_1,DSV$AmpSmNno20_2))
DSV$AmpSmNno40Hz = rowMeans(cbind(DSV$AmpSmNno40_1,DSV$AmpSmNno40_2))
DSV$AmpSmNno80Hz = rowMeans(cbind(DSV$AmpSmNno80_1,DSV$AmpSmNno80_2))
DSV$AmpSmNlo20Hz = rowMeans(cbind(DSV$AmpSmNlo20_1,DSV$AmpSmNlo20_2))
DSV$AmpSmNlo40Hz = rowMeans(cbind(DSV$AmpSmNlo40_1,DSV$AmpSmNlo40_2))
DSV$AmpSmNlo80Hz = rowMeans(cbind(DSV$AmpSmNlo80_1,DSV$AmpSmNlo80_2))
DSV$AmpSmNhi20Hz = rowMeans(cbind(DSV$AmpSmNhi20_1,DSV$AmpSmNhi20_2))
DSV$AmpSmNhi40Hz = rowMeans(cbind(DSV$AmpSmNhi40_1,DSV$AmpSmNhi40_2))
DSV$AmpSmNhi80Hz = rowMeans(cbind(DSV$AmpSmNhi80_1,DSV$AmpSmNhi80_2))

# 
# # Amp S raw
# D$AmpSno20Hz = rowMeans(cbind(D$AmpSno20_1,D$AmpSno20_2))
# D$AmpSno40Hz = rowMeans(cbind(D$AmpSno40_1,D$AmpSno40_2))
# D$AmpSno80Hz = rowMeans(cbind(D$AmpSno80_1,D$AmpSno80_2))
# D$AmpSlo20Hz = rowMeans(cbind(D$AmpSlo20_1,D$AmpSlo20_2))
# D$AmpSlo40Hz = rowMeans(cbind(D$AmpSlo40_1,D$AmpSlo40_2))
# D$AmpSlo80Hz = rowMeans(cbind(D$AmpSlo80_1,D$AmpSlo80_2))
# D$AmpShi20Hz = rowMeans(cbind(D$AmpShi20_1,D$AmpShi20_2))
# D$AmpShi40Hz = rowMeans(cbind(D$AmpShi40_1,D$AmpShi40_2))
# D$AmpShi80Hz = rowMeans(cbind(D$AmpShi80_1,D$AmpShi80_2))
# 
# # Amp N raw
# D$AmpNno20Hz = rowMeans(cbind(D$AmpNno20_1,D$AmpNno20_2))
# D$AmpNno40Hz = rowMeans(cbind(D$AmpNno40_1,D$AmpNno40_2))
# D$AmpNno80Hz = rowMeans(cbind(D$AmpNno80_1,D$AmpNno80_2))
# D$AmpNlo20Hz = rowMeans(cbind(D$AmpNlo20_1,D$AmpNlo20_2))
# D$AmpNlo40Hz = rowMeans(cbind(D$AmpNlo40_1,D$AmpNlo40_2))
# D$AmpNlo80Hz = rowMeans(cbind(D$AmpNlo80_1,D$AmpNlo80_2))
# D$AmpNhi20Hz = rowMeans(cbind(D$AmpNhi20_1,D$AmpNhi20_2))
# D$AmpNhi40Hz = rowMeans(cbind(D$AmpNhi40_1,D$AmpNhi40_2))
# D$AmpNhi80Hz = rowMeans(cbind(D$AmpNhi80_1,D$AmpNhi80_2))
# 
# # Amp SNR raw
# D$AmpSNRno20Hz = rowMeans(cbind(D$AmpSNRno20_1,D$AmpSNRno20_2))
# D$AmpSNRno40Hz = rowMeans(cbind(D$AmpSNRno40_1,D$AmpSNRno40_2))
# D$AmpSNRno80Hz = rowMeans(cbind(D$AmpSNRno80_1,D$AmpSNRno80_2))
# D$AmpSNRlo20Hz = rowMeans(cbind(D$AmpSNRlo20_1,D$AmpSNRlo20_2))
# D$AmpSNRlo40Hz = rowMeans(cbind(D$AmpSNRlo40_1,D$AmpSNRlo40_2))
# D$AmpSNRlo80Hz = rowMeans(cbind(D$AmpSNRlo80_1,D$AmpSNRlo80_2))
# D$AmpSNRhi20Hz = rowMeans(cbind(D$AmpSNRhi20_1,D$AmpSNRhi20_2))
# D$AmpSNRhi40Hz = rowMeans(cbind(D$AmpSNRhi40_1,D$AmpSNRhi40_2))
# D$AmpSNRhi80Hz = rowMeans(cbind(D$AmpSNRhi80_1,D$AmpSNRhi80_2))
```

```{r create EEG ITC variables, echo = rout}
# ITC S-N raw

# ASSR Study 1
# the numbers 1 to 4 refer to different blocks

DSIV_s1$ItcSmNlo = rowMeans(cbind(DSIV_s1$ItcSmNlo1,DSIV_s1$ItcSmNlo2,DSIV_s1$ItcSmNlo3,DSIV_s1$ItcSmNlo4))
DSIV_s1$ItcSmNhi = rowMeans(cbind(DSIV_s1$ItcSmNhi1,DSIV_s1$ItcSmNhi2,DSIV_s1$ItcSmNhi3,DSIV_s1$ItcSmNhi4))

# ASSR Study 2
# the numbers 1 to 4 refer to different blocks
DSIV_s2$ItcSmNno = rowMeans(cbind(DSIV_s2$ItcSmNno1,DSIV_s2$ItcSmNno2,DSIV_s2$ItcSmNno3,DSIV_s2$ItcSmNno4))
DSIV_s2$ItcSmNlo = rowMeans(cbind(DSIV_s2$ItcSmNlo1,DSIV_s2$ItcSmNlo2,DSIV_s2$ItcSmNlo3,DSIV_s2$ItcSmNlo4))
DSIV_s2$ItcSmNhi = rowMeans(cbind(DSIV_s2$ItcSmNhi1,DSIV_s2$ItcSmNhi2,DSIV_s2$ItcSmNhi3,DSIV_s2$ItcSmNhi4))
DSIV_s2$ItcSmNvh = rowMeans(cbind(DSIV_s2$ItcSmNvh1,DSIV_s2$ItcSmNvh2,DSIV_s2$ItcSmNvh3,DSIV_s2$ItcSmNvh4))

# ASSR2
# the numbers 1 to 2 refer to different blocks
DSV$ItcSmNno20Hz = rowMeans(cbind(DSV$ItcSmNno20_1,DSV$ItcSmNno20_2))
DSV$ItcSmNno40Hz = rowMeans(cbind(DSV$ItcSmNno40_1,DSV$ItcSmNno40_2))
DSV$ItcSmNno80Hz = rowMeans(cbind(DSV$ItcSmNno80_1,DSV$ItcSmNno80_2))
DSV$ItcSmNlo20Hz = rowMeans(cbind(DSV$ItcSmNlo20_1,DSV$ItcSmNlo20_2))
DSV$ItcSmNlo40Hz = rowMeans(cbind(DSV$ItcSmNlo40_1,DSV$ItcSmNlo40_2))
DSV$ItcSmNlo80Hz = rowMeans(cbind(DSV$ItcSmNlo80_1,DSV$ItcSmNlo80_2))
DSV$ItcSmNhi20Hz = rowMeans(cbind(DSV$ItcSmNhi20_1,DSV$ItcSmNhi20_2))
DSV$ItcSmNhi40Hz = rowMeans(cbind(DSV$ItcSmNhi40_1,DSV$ItcSmNhi40_2))
DSV$ItcSmNhi80Hz = rowMeans(cbind(DSV$ItcSmNhi80_1,DSV$ItcSmNhi80_2))


# # the numbers 1 to 2 refer to different blocks
# 
# # ITC S-N raw
# D$ItcSmNno20Hz = rowMeans(cbind(D$ItcSmNno20_1,D$ItcSmNno20_2))
# D$ItcSmNno40Hz = rowMeans(cbind(D$ItcSmNno40_1,D$ItcSmNno40_2))
# D$ItcSmNno80Hz = rowMeans(cbind(D$ItcSmNno80_1,D$ItcSmNno80_2))
# D$ItcSmNlo20Hz = rowMeans(cbind(D$ItcSmNlo20_1,D$ItcSmNlo20_2))
# D$ItcSmNlo40Hz = rowMeans(cbind(D$ItcSmNlo40_1,D$ItcSmNlo40_2))
# D$ItcSmNlo80Hz = rowMeans(cbind(D$ItcSmNlo80_1,D$ItcSmNlo80_2))
# D$ItcSmNhi20Hz = rowMeans(cbind(D$ItcSmNhi20_1,D$ItcSmNhi20_2))
# D$ItcSmNhi40Hz = rowMeans(cbind(D$ItcSmNhi40_1,D$ItcSmNhi40_2))
# D$ItcSmNhi80Hz = rowMeans(cbind(D$ItcSmNhi80_1,D$ItcSmNhi80_2))
# 
# # ITC S raw
# D$ItcSno20Hz = rowMeans(cbind(D$ItcSno20_1,D$ItcSno20_2))
# D$ItcSno40Hz = rowMeans(cbind(D$ItcSno40_1,D$ItcSno40_2))
# D$ItcSno80Hz = rowMeans(cbind(D$ItcSno80_1,D$ItcSno80_2))
# D$ItcSlo20Hz = rowMeans(cbind(D$ItcSlo20_1,D$ItcSlo20_2))
# D$ItcSlo40Hz = rowMeans(cbind(D$ItcSlo40_1,D$ItcSlo40_2))
# D$ItcSlo80Hz = rowMeans(cbind(D$ItcSlo80_1,D$ItcSlo80_2))
# D$ItcShi20Hz = rowMeans(cbind(D$ItcShi20_1,D$ItcShi20_2))
# D$ItcShi40Hz = rowMeans(cbind(D$ItcShi40_1,D$ItcShi40_2))
# D$ItcShi80Hz = rowMeans(cbind(D$ItcShi80_1,D$ItcShi80_2))
# 
# # ITC N raw
# D$ItcNno20Hz = rowMeans(cbind(D$ItcNno20_1,D$ItcNno20_2))
# D$ItcNno40Hz = rowMeans(cbind(D$ItcNno40_1,D$ItcNno40_2))
# D$ItcNno80Hz = rowMeans(cbind(D$ItcNno80_1,D$ItcNno80_2))
# D$ItcNlo20Hz = rowMeans(cbind(D$ItcNlo20_1,D$ItcNlo20_2))
# D$ItcNlo40Hz = rowMeans(cbind(D$ItcNlo40_1,D$ItcNlo40_2))
# D$ItcNlo80Hz = rowMeans(cbind(D$ItcNlo80_1,D$ItcNlo80_2))
# D$ItcNhi20Hz = rowMeans(cbind(D$ItcNhi20_1,D$ItcNhi20_2))
# D$ItcNhi40Hz = rowMeans(cbind(D$ItcNhi40_1,D$ItcNhi40_2))
# D$ItcNhi80Hz = rowMeans(cbind(D$ItcNhi80_1,D$ItcNhi80_2))
# 
# # ITC SNR raw
# D$ItcSNRno20Hz = rowMeans(cbind(D$ItcSNRno20_1,D$ItcSNRno20_2))
# D$ItcSNRno40Hz = rowMeans(cbind(D$ItcSNRno40_1,D$ItcSNRno40_2))
# D$ItcSNRno80Hz = rowMeans(cbind(D$ItcSNRno80_1,D$ItcSNRno80_2))
# D$ItcSNRlo20Hz = rowMeans(cbind(D$ItcSNRlo20_1,D$ItcSNRlo20_2))
# D$ItcSNRlo40Hz = rowMeans(cbind(D$ItcSNRlo40_1,D$ItcSNRlo40_2))
# D$ItcSNRlo80Hz = rowMeans(cbind(D$ItcSNRlo80_1,D$ItcSNRlo80_2))
# D$ItcSNRhi20Hz = rowMeans(cbind(D$ItcSNRhi20_1,D$ItcSNRhi20_2))
# D$ItcSNRhi40Hz = rowMeans(cbind(D$ItcSNRhi40_1,D$ItcSNRhi40_2))
# D$ItcSNRhi80Hz = rowMeans(cbind(D$ItcSNRhi80_1,D$ItcSNRhi80_2))
```

## Means and 95% CIs {.tabset}
Plots and tables for each study.  
Study IV s1 tested 40-Hz ASSRs in low and high load  
Study IV s2 tested 40-Hz ASSRs in no, low, and high load  
Study V tested 20-, 40-, and 80-Hz ASSRs in no, low and high load  

### Study IV s1: 40-Hz ASSRs {.tabset}
Activity at 80 Hz (second harmonic) for 40-Hz ASSRs

#### Ampl SmN {.tabset}
Amplitude signal minus noise (SmN)  

##### plot
```{r plot AmpSmN SIV_s1, echo = rout}
iv = "AmpSmN"

Dtmp = getdiffs_SIV_s1(DSIV_s1, iv = iv)
myylim = c(-0.1, 0.1)#max(Dtmp)) 
Dtmp = Dtmp[,c(3:5)]#[,c(10:27)]
Dtmp = cbind(DSIV_s1$fp, Dtmp)
colnames(Dtmp)[1] =  c('fp', 'low', 'high', 'low-high')

bp1a = plotoverlay(dm = Dtmp,lbl = paste0("ASSR study 1"), dvy = "Mean SmN amplitude (µV)", myylim)

grid.arrange(bp1a, ncol = 3)

ggsave(file.path(dir_fig,"figure_amp_2ndharm_ASSRStudy1.jpg"), bp1a , dpi = 600, width = 3, height = 4)
ggsave(file.path(dir_fig,"figure_amp_2ndharm_ASSRStudy1.pdf"), bp1a , dpi = 600, width = 3, height = 4)

Dtmp_amp = Dtmp # save for later
```
##### table
```{r contrasts AmpSmN SIV_s1, echo = rout}
iv = "AmpSmN"
Dtmp = getdiffs_SIV_s1(DSIV_s1, iv = iv)
Dtmp = tableCIs(Dtmp[,-c(1:2)])
Dtmp %>%
  kable(digits = 3, caption = "Study IV s1") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = 'left')
```


#### ITC SmN  {.tabset}
Intertrial coherence signal minus noise (SmN) 

##### plot
```{r plot ITCSmN SIV_s1, echo = rout}
iv = "ItcSmN"
Dtmp = getdiffs_SIV_s1(DSIV_s1, iv = iv)
myylim = c(-0.3, 0.3)#max(Dtmp)) 
Dtmp = Dtmp[,c(3:5)]#[,c(10:27)]
Dtmp = cbind(DSIV_s1$fp, Dtmp)
colnames(Dtmp)[1] =  c('fp', 'low', 'high', 'low-high')

bp1a = plotoverlay(dm = Dtmp,lbl = paste0("ASSR study 1"), dvy = "Mean SmN ITC", myylim)
grid.arrange(bp1a, ncol = 3)

ggsave(file.path(dir_fig,"figure_itc_2ndharm_ASSRStudy1.jpg"), bp1a, dpi = 600, width = 3, height = 4)
ggsave(file.path(dir_fig,"figure_itc_2ndharm_ASSRStudy1.pdf"), bp1a, dpi = 600, width = 3, height = 4)

Dtmp_itc = Dtmp # save for later
```

##### table
```{r contrasts ITCSmN SIV_s1, echo = rout}
Dtmp = getdiffs_SIV_s1(DSIV_s1, iv = iv)
Dtmp = tableCIs(Dtmp[,-c(1:2)])
Dtmp %>%
  kable(digits = 3, caption = "Study IV s1") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = 'left')
```

### Study IV s2: 40-Hz ASSRs {.tabset}
Activity at 80 Hz (second harmonic) for 40-Hz ASSRs

#### Ampl SmN {.tabset}
Amplitude signal minus noise (SmN)  

##### plot
```{r plot AmpSmN SIV_s2, echo = rout}
iv = "AmpSmN"
Dtmp2 = getdiffs_SIV_s2(DSIV_s2, iv = iv)
myylim = c(-0.1, 0.1)#max(Dtmp2)) 
Dtmp2 = Dtmp2[,c(4:9)]#[,c(10:27)]
Dtmp2 = cbind(DSIV_s2$fp, Dtmp2)
colnames(Dtmp2)[1] =  c('fp', 'no', 'low', 'high', 'no-low','no-high','low-high')

bp1b = plotoverlay(dm = Dtmp2,lbl = paste0("ASSR study 2"), dvy = "Mean SmN amplitude (µV)", myylim)
grid.arrange(bp1b, ncol = 3)

ggsave(file.path(dir_fig,"figure_amp_2ndharm_ASSRStudy2.jpg"), bp1b, dpi = 600, width = 3, height = 4)
ggsave(file.path(dir_fig,"figure_amp_2ndharm_ASSRStudy2.pdf"), bp1b, dpi = 600, width = 3, height = 4)

Dtmp2_amp = Dtmp2 # save for later
```

##### table
```{r contrasts AmpSmN SIV_s2, echo = rout}
iv = "AmpSmN"
Dtmp2 = getdiffs_SIV_s2(DSIV_s2, iv = iv)
Dtmp2 = tableCIs(Dtmp2[,-c(1:3)])
Dtmp2 %>%
  kable(digits = 3, caption = "Study IV s2") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = 'left')
```

#### ITC SmN  {.tabset}
Intertrial coherence signal minus noise (SmN) 

##### plot
```{r plot ITCSmN SIV_s2, echo = rout}
iv = "ItcSmN"
Dtmp2 = getdiffs_SIV_s2(DSIV_s2, iv = iv)
myylim = c(-0.3, 0.3)#max(Dtmp2)) 
Dtmp2 = Dtmp2[,c(4:9)]#[,c(10:27)]
Dtmp2 = cbind(DSIV_s2$fp, Dtmp2)
colnames(Dtmp2)[1] =  c('fp', 'no', 'low', 'high', 'no-low','no-high','low-high')

bp1b = plotoverlay(dm = Dtmp2,lbl = paste0("ASSR study 2"), dvy = "Mean SmN ITC", myylim)
grid.arrange(bp1b, ncol = 3)

ggsave(file.path(dir_fig,"figure_itc_2ndharm_ASSRStudy2.jpg"), bp1b, dpi = 600, width = 3, height = 4)
ggsave(file.path(dir_fig,"figure_itc_2ndharm_ASSRStudy2.pdf"), bp1b, dpi = 600, width = 3, height = 4)

Dtmp2_itc = Dtmp2 # save for later
```

##### table
```{r contrasts for ITCSmN, echo = rout}
iv = "ItcSmN"
Dtmp2 = getdiffs_SIV_s2(DSIV_s2, iv = iv)
Dtmp2 = tableCIs(Dtmp2[,-c(1:3)])
Dtmp2 %>%
  kable(digits = 3, caption = "Study IV s2") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = 'left')
```

### Study V: 20-, 40-, and 80-Hz ASSRs {.tabset}
Activity at: 
  40 Hz (second harmonic) for 20-Hz ASSRs, 
  80 Hz (second harmonic) for 40-Hz ASSRs,
  160 Hz (second harmonic) for 80-Hz ASSRs

#### Ampl SmN {.tabset}
Amplitude signal minus noise (SmN)  

##### plot
```{r plot AmpSmN SV, echo = rout}
iv = "AmpSmN"
Dtmp3 = getdiffs_SV(DSV, iv = iv)
myylim = c(min(Dtmp3), max(Dtmp3)) 
Dtmp3 = Dtmp3[,c(10:27)]
Dtmp3 = cbind(DSV$fp, Dtmp3)

Dtmp3a = Dtmp3[,c(1,2:7)]
colnames(Dtmp3a) = c('fp', 'no', 'low', 'high', 'no-low','no-high','low-high')
bp3a = plotoverlay(dm = Dtmp3a,lbl = paste0("20 Hz"), dvy = "Mean SmN amplitude (µV)", myylim)
Dtmp3b = Dtmp3[,c(1,8:13)]
colnames(Dtmp3b) = c('fp', 'no', 'low', 'high', 'no-low','no-high','low-high')
bp3b = plotoverlay(dm = Dtmp3b,lbl = paste0("40 Hz"), dvy = "", myylim)
Dtmp3c = Dtmp3[,c(1,14:19)]
colnames(Dtmp3c) = c('fp', 'no', 'low', 'high', 'no-low','no-high','low-high')
bp3c = plotoverlay(dm = Dtmp3c,lbl = paste0("80 Hz"), dvy = "", myylim)
grid.arrange(bp3a, bp3b, bp3c, ncol = 3)
bp3 = arrangeGrob(bp3a, bp3b, bp3c, ncol = 3)

ggsave(file.path(dir_fig,"figure_amp_2ndharm_ASSR2.jpg"), bp3, dpi = 600, width = 7, height = 4)
ggsave(file.path(dir_fig,"figure_amp_2ndharm_ASSR2.pdf"), bp3, dpi = 600, width = 7, height = 4)

Dtmp3_amp = Dtmp3 # save for later
colnames(Dtmp3_amp)[1] = "fp"
```

##### table
```{r contrasts AmpSmN SV, echo = rout}
iv = "AmpSmN"
Dtmp3 = getdiffs_SV(DSV, iv = iv)
Dtmp3 = tableCIs(Dtmp3[,-c(1:9)])
Dtmp3 %>%
  kable(digits = 3, caption = "Study V") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = 'left')
```

#### ITC SmN  {.tabset}
Intertrial coherence signal minus noise (SmN) 

##### plot
```{r plot ITCSmN SV, echo = rout}
iv = "ItcSmN"

Dtmp3 = getdiffs_SV(DSV, iv = iv)
myylim = c(-0.3, 0.5) 
Dtmp3 = Dtmp3[,c(10:27)]
Dtmp3 = cbind(DSV$fp, Dtmp3)

Dtmp3a = Dtmp3[,c(1,2:7)]
colnames(Dtmp3a) = c('fp', 'no', 'low', 'high', 'no-low','no-high','low-high')
bp3a = plotoverlay(dm = Dtmp3a,lbl = paste0("20 Hz"), dvy = "Mean SmN ITC", myylim)
Dtmp3b = Dtmp3[,c(1,8:13)]
colnames(Dtmp3b) = c('fp', 'no', 'low', 'high', 'no-low','no-high','low-high')
bp3b = plotoverlay(dm = Dtmp3b,lbl = paste0("40 Hz"), dvy = "", myylim)
Dtmp3c = Dtmp3[,c(1,14:19)]
colnames(Dtmp3c) = c('fp', 'no', 'low', 'high', 'no-low','no-high','low-high')
bp3c = plotoverlay(dm = Dtmp3c,lbl = paste0("80 Hz"), dvy = "", myylim)
grid.arrange(bp3a, bp3b, bp3c, ncol = 3)
bp3 = arrangeGrob(bp3a, bp3b, bp3c, ncol = 3)

ggsave(file.path(dir_fig,"figure_itc_2ndharm_ASSR2.jpg"), bp3, dpi = 600, width = 7, height = 4)
ggsave(file.path(dir_fig,"figure_itc_2ndharm_ASSR2.pdf"), bp3, dpi = 600, width = 7, height = 4)

Dtmp3_itc = Dtmp3 # save for later
colnames(Dtmp3_itc)[1] = "fp"
```

##### table
```{r contrasts ITCSmN SV, echo = rout}
iv = "ItcSmN"

Dtmp3 = getdiffs_SV(DSV, iv = iv)
Dtmp3 = tableCIs(Dtmp3[,-c(1:9)])
Dtmp3 %>%
  kable(digits = 3, caption = "Study V") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = 'left')
```

## BF for Study V {.tabset}
Study V included 3 different modulation frequencies: 20, 40, and 80 Hz.
Below are the results for 2nd harmonic for each frequency separately and 
averaged across all frequencies

To conduct BF analyses, we defined the upper limits on the basis of the present data, separately for each measure and frequency.    


**Low minus high**  
  One analysis considered **low load** as the baseline, and the H1 model was defined as a uniform distribution between 0 (as lower limit, LL) and the present mean of low load (as upper limit, UL).  

Low minus high = load effect  

**No minus low/high**  
  Other analyses considered **no load** as the baseline, and the H1 model was defined as a uniform distribution between 0 (as lower limit, LL) and the present mean of no load (as upper limit, UL).  

No minus low = task effect  
No minus high = combined effect of task and load  


In the table, LL and UL refer to the 95% CIs of the means (and not to the LL and UL of the H1 models).  

```{r select data from Study V, echo = rout}
# ASSR2 20 Hz
Dtmpa3_20 = subset(Dtmp3_amp, 
               select=c(fp, no20Hz, lo20Hz, hi20Hz))
colnames(Dtmpa3_20) = c('fp', 'AmpSmNno', 'AmpSmNlo', 'AmpSmNhi')
Dtmpi3_20 = subset(Dtmp3_itc, 
               select=c(no20Hz, lo20Hz, hi20Hz))
colnames(Dtmpi3_20) = c('ItcSmNno', 'ItcSmNlo', 'ItcSmNhi')
Dtmp3_20 = cbind(Dtmpa3_20, Dtmpi3_20)
Dtmp3_20$freq = 20

# ASSR2 40 Hz
Dtmpa3_40 = subset(Dtmp3_amp, 
               select=c(fp, no40Hz, lo40Hz, hi40Hz))
colnames(Dtmpa3_40) = c('fp', 'AmpSmNno', 'AmpSmNlo', 'AmpSmNhi')
Dtmpi3_40 = subset(Dtmp3_itc, 
               select=c(no40Hz, lo40Hz, hi40Hz))
colnames(Dtmpi3_40) = c('ItcSmNno', 'ItcSmNlo', 'ItcSmNhi')
Dtmp3_40 = cbind(Dtmpa3_40, Dtmpi3_40)
Dtmp3_40$study = 40

# ASSR2 80 Hz
Dtmpa3_80 = subset(Dtmp3_amp, 
               select=c(fp, no80Hz, lo80Hz, hi80Hz))
colnames(Dtmpa3_80) = c('fp', 'AmpSmNno', 'AmpSmNlo', 'AmpSmNhi')
Dtmpi3_80 = subset(Dtmp3_itc, 
               select=c(no80Hz, lo80Hz, hi80Hz))
colnames(Dtmpi3_80) = c('ItcSmNno', 'ItcSmNlo', 'ItcSmNhi')
Dtmp3_80 = cbind(Dtmpa3_80, Dtmpi3_80)
Dtmp3_80$study = 80

# combined amp
Davg_no = subset(Dtmp3_amp, 
               select=c(no20Hz, no40Hz, no80Hz))

Davg_lo = subset(Dtmp3_amp, 
               select=c(lo20Hz, lo40Hz, lo80Hz))

Davg_hi = subset(Dtmp3_amp, 
               select=c(hi20Hz, hi40Hz, hi80Hz))

Davg = data.frame(Dtmp3_amp['fp'])
Davg$no = rowMeans(Davg_no)
Davg$lo = rowMeans(Davg_lo)
Davg$hi = rowMeans(Davg_hi)
colnames(Davg) = c('fp', 'AmpSmNno', 'AmpSmNlo', 'AmpSmNhi')


# combined itc
Davgi_no = subset(Dtmp3_itc, 
               select=c(no20Hz, no40Hz, no80Hz))

Davgi_lo = subset(Dtmp3_itc, 
               select=c(lo20Hz, lo40Hz, lo80Hz))

Davgi_hi = subset(Dtmp3_itc, 
               select=c(hi20Hz, hi40Hz, hi80Hz))

Davgi = data.frame(Dtmp3_amp['fp'])
Davgi$no = rowMeans(Davgi_no)
Davgi$lo = rowMeans(Davgi_lo)
Davgi$hi = rowMeans(Davgi_hi)
colnames(Davgi) = c('fp', 'ItcSmNno', 'ItcSmNlo', 'ItcSmNhi')
```

### load effect: low minus high
High load is used as the upper limit of the H1 model.  
H1 model:  
LL = 0  
UL = low load  
In the table, LL and UL refer to the 95% CIs of the means (and not to the LL and UL of the H1 models).
```{r Study V data hiMlo, echo = rout}
DBF10 = numeric()

# create matrix with measure, study, n, mean high load, 
# diff hiMlo, LL 95%CI, UL 95%CI, BF10 hiMlo, BF01 hiMlo,
LL = 0

# amp
# 20 Hz
UL = mean(Dtmp3_20$AmpSmNlo)
tmp = Dtmp3_20$AmpSmNlo-Dtmp3_20$AmpSmNhi
DBF10 = rbind(DBF10, c('20 Hz','Amp', nrow(Dtmp3_20), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 40 Hz
UL = mean(Dtmp3_40$AmpSmNlo)
tmp = Dtmp3_40$AmpSmNlo-Dtmp3_40$AmpSmNhi
DBF10 = rbind(DBF10, c('40 Hz','Amp', nrow(Dtmp3_40), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 80 Hz
UL = mean(Dtmp3_80$AmpSmNlo)
tmp = Dtmp3_80$AmpSmNlo-Dtmp3_80$AmpSmNhi
DBF10 = rbind(DBF10, c('80 Hz', 'Amp', nrow(Dtmp3_80), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(Davg$AmpSmNlo)
tmp = Davg$AmpSmNlo-Davg$AmpSmNhi
DBF10 = rbind(DBF10, c('Combined','Amp', nrow(Davg), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# itc
# 20 Hz
UL = mean(Dtmp3_20$ItcSmNlo)
tmp = Dtmp3_20$ItcSmNlo-Dtmp3_20$ItcSmNhi
DBF10 = rbind(DBF10, c('20 Hz','Itc', nrow(Dtmp3_20), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 40 Hz
UL = mean(Dtmp3_40$ItcSmNlo)
tmp = Dtmp3_40$ItcSmNlo-Dtmp3_40$ItcSmNhi
DBF10 = rbind(DBF10, c('40 Hz','Itc', nrow(Dtmp3_40), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 80 Hz
UL = mean(Dtmp3_80$ItcSmNlo)
tmp = Dtmp3_80$ItcSmNlo-Dtmp3_80$ItcSmNhi
DBF10 = rbind(DBF10, c('80 Hz', 'Itc', nrow(Dtmp3_80), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(Davgi$ItcSmNlo)
tmp = Davgi$ItcSmNlo-Davgi$ItcSmNhi
DBF10 = rbind(DBF10, c('Combined','Itc', nrow(Davgi), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))


DBF10 = as.data.frame(DBF10)
colnames(DBF10)=c('Freq','Measure','N','Mhi',
                  'M-loMhi','LL-loMhi','UL-loMhi','BF10-loMhi','BF01-loMhi')

# convert character to numeric
i = 3:9
DBF10[, i] = apply(DBF10[,i],2, function(x) as.numeric(as.character(x)))
DBF10 %>%
  kable(digits = 3,
        col.names = c('Freq','Measure','N','Mean',
                      'Mean','LL', 'UL', 'BF10', 'BF01')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = 'left') %>%
  add_header_above(c(" " = 3, "low" = 1, "low minus high" = 5)) %>%
  row_spec(c(4,8), bold = T)
```

### task effect: no minus low
Low load is used as the upper limit of the H1 model.  
H1 model:  
LL = 0  
UL = no load  
In the table, LL and UL refer to the 95% CIs of the means (and not to the LL and UL of the H1 models).  
```{r Study V data loMno, echo = rout}
# compare low with no load
DBF10 = numeric()

# create matrix with measure, study, n, mean low load, 
# diff loMhi, LL 95%CI, UL 95%CI, BF01 loMhi
LL = 0

# amp
# 20 Hz
UL = mean(Dtmp3_20$AmpSmNno)
tmp = Dtmp3_20$AmpSmNno-Dtmp3_20$AmpSmNlo
DBF10 = rbind(DBF10, c('20 Hz','Amp', nrow(Dtmp3_20), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 40 Hz
UL = mean(Dtmp3_40$AmpSmNno)
tmp = Dtmp3_40$AmpSmNno-Dtmp3_40$AmpSmNlo
DBF10 = rbind(DBF10, c('40 Hz','Amp', nrow(Dtmp3_40), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 80 Hz
UL = mean(Dtmp3_80$AmpSmNno)
tmp = Dtmp3_80$AmpSmNno-Dtmp3_80$AmpSmNlo
DBF10 = rbind(DBF10, c('80 Hz', 'Amp', nrow(Dtmp3_80), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(Davg$AmpSmNno)
tmp = Davg$AmpSmNno-Davg$AmpSmNlo
DBF10 = rbind(DBF10, c('Combined','Amp', nrow(Davg), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# itc
# 20 Hz
UL = mean(Dtmp3_20$ItcSmNno)
tmp = Dtmp3_20$ItcSmNno-Dtmp3_20$ItcSmNlo
DBF10 = rbind(DBF10, c('20 Hz','Itc', nrow(Dtmp3_20), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 40 Hz
UL = mean(Dtmp3_40$ItcSmNno)
tmp = Dtmp3_40$ItcSmNno-Dtmp3_40$ItcSmNlo
DBF10 = rbind(DBF10, c('40 Hz','Itc', nrow(Dtmp3_40), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 80 Hz
UL = mean(Dtmp3_80$ItcSmNno)
tmp = Dtmp3_80$ItcSmNno-Dtmp3_80$ItcSmNlo
DBF10 = rbind(DBF10, c('80 Hz', 'Itc', nrow(Dtmp3_80), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(Davgi$ItcSmNno)
tmp = Davgi$ItcSmNno-Davgi$ItcSmNlo
DBF10 = rbind(DBF10, c('Combined','Itc', nrow(Davgi), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))


DBF10 = as.data.frame(DBF10)
colnames(DBF10)=c('Freq','Measure','N','Mno',
                  'M-noMlo','LL-noMlo','UL-noMlo','BF10-noMlo','BF01-noMlo')

# convert character to numeric
i = 3:9
DBF10[, i] = apply(DBF10[,i],2, function(x) as.numeric(as.character(x)))
DBF10 %>%
  kable(digits = 3,
        col.names = c('Freq','Measure','N','Mean',
                      'Mean','LL', 'UL', 'BF10', 'BF01')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = 'left') %>%
  add_header_above(c(" " = 3, "no" = 1, "no minus low" = 5)) %>%
  row_spec(c(4,8), bold = T)
```
### combined effect: no minus high
High load is used as the upper limit of the H1 model.  
H1 model:  
LL = 0  
UL = no load  

In the table, LL and UL refer to the 95% CIs of the means (and not to the LL and UL of the H1 models).
```{r Study V data hiMno, echo = rout}

DBF10 = numeric()

# create matrix with measure, study, n, mean no load, 
# diff hiMno, LL 95%CI, UL 95%CI, BF10 hiMno, BF01 hiMno,
# diff hiMlo, LL 95%CI, UL 95%CI, BF10 hiMlo, BF01 hiMlo,
LL = 0

# amp
# 20 Hz
UL = mean(Dtmp3_20$AmpSmNno)
tmp = Dtmp3_20$AmpSmNno-Dtmp3_20$AmpSmNhi
DBF10 = rbind(DBF10, c('20 Hz','Amp', nrow(Dtmp3_20), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 40 Hz
UL = mean(Dtmp3_40$AmpSmNno)
tmp = Dtmp3_40$AmpSmNno-Dtmp3_40$AmpSmNhi
DBF10 = rbind(DBF10, c('40 Hz','Amp', nrow(Dtmp3_40), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 80 Hz
UL = mean(Dtmp3_80$AmpSmNno)
tmp = Dtmp3_80$AmpSmNno-Dtmp3_80$AmpSmNhi
DBF10 = rbind(DBF10, c('80 Hz', 'Amp', nrow(Dtmp3_80), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(Davg$AmpSmNno)
tmp = Davg$AmpSmNno-Davg$AmpSmNhi
DBF10 = rbind(DBF10, c('Combined','Amp', nrow(Davg), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# itc
# 20 Hz
UL = mean(Dtmp3_20$ItcSmNno)
tmp = Dtmp3_20$ItcSmNno-Dtmp3_20$ItcSmNhi
DBF10 = rbind(DBF10, c('20 Hz','Itc', nrow(Dtmp3_20), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 40 Hz
UL = mean(Dtmp3_40$ItcSmNno)
tmp = Dtmp3_40$ItcSmNno-Dtmp3_40$ItcSmNhi
DBF10 = rbind(DBF10, c('40 Hz','Itc', nrow(Dtmp3_40), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# 80 Hz
UL = mean(Dtmp3_80$ItcSmNno)
tmp = Dtmp3_80$ItcSmNno-Dtmp3_80$ItcSmNhi
DBF10 = rbind(DBF10, c('80 Hz', 'Itc', nrow(Dtmp3_80), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(Davgi$ItcSmNno)
tmp = Davgi$ItcSmNno-Davgi$ItcSmNhi
DBF10 = rbind(DBF10, c('Combined','Itc', nrow(Davgi), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))


DBF10 = as.data.frame(DBF10)
colnames(DBF10)=c('Freq','Measure','N','Mno',
                  'M-noMhi','LL-noMhi','UL-noMhi','BF10-noMhi','BF01-noMhi')

# convert character to numeric
i = 3:9
DBF10[, i] = apply(DBF10[,i],2, function(x) as.numeric(as.character(x)))
DBF10 %>%
  kable(digits = 3,
        col.names = c('Freq','Measure','N','Mean',
                      'Mean','LL', 'UL', 'BF10', 'BF01')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = 'left') %>%
  add_header_above(c(" " = 3, "no" = 1, "no minus high" = 5)) %>%
  row_spec(c(4,8), bold = T)
```


## BF for 40-Hz: combined data {.tabset}
Study IV s1 (N = 43) in Szychowska & Wiens (2020). This study included **low and high** load.    

Study IV s2 (N = 45) in Szychowska & Wiens (2020). This study included **no, low, high, and very high** load.

Study V (N = 33)  in Szychowska & Wiens (2020). This study included **no, low, high** load.
```{r select 40 Hz data, echo = rout}
# ASSR Study1
Dtmpa1 = subset(Dtmp_amp, 
               select=c(fp, lo, hi))
colnames(Dtmpa1) = c('fp', 'AmpSmNlo', 'AmpSmNhi')
Dtmpi1 = subset(Dtmp_itc, 
               select=c(lo, hi))
colnames(Dtmpi1) = c('ItcSmNlo', 'ItcSmNhi')
Dtmp1 = cbind(Dtmpa1, Dtmpi1)
Dtmp1$study = 'Study IV s1'

# ASSR Study2
Dtmpa2 = subset(Dtmp2_amp, 
               select=c(fp, no, lo, hi))
colnames(Dtmpa2) = c('fp', 'AmpSmNno', 'AmpSmNlo', 'AmpSmNhi')
Dtmpi2 = subset(Dtmp2_itc, 
               select=c(no, lo, hi))
colnames(Dtmpi2) = c('ItcSmNno', 'ItcSmNlo', 'ItcSmNhi')
Dtmp2 = cbind(Dtmpa2, Dtmpi2)
Dtmp2$study = 'Study IV s2'

# ASSR2
Dtmpa3 = subset(Dtmp3_amp, 
               select=c(fp, no40Hz, lo40Hz, hi40Hz))
colnames(Dtmpa3) = c('fp', 'AmpSmNno', 'AmpSmNlo', 'AmpSmNhi')
Dtmpi3 = subset(Dtmp3_itc, 
               select=c(no40Hz, lo40Hz, hi40Hz))
colnames(Dtmpi3) = c('ItcSmNno', 'ItcSmNlo', 'ItcSmNhi')
Dtmp3 = cbind(Dtmpa3, Dtmpi3)
Dtmp3$study = 'Study V'


Dall = merge(Dtmp1, Dtmp2, all = T)
Dall = merge(Dall, Dtmp3, all = T)

D2and3 = merge(Dtmp2, Dtmp3, all = T)
```

### load effect: low minus high
Low load is used as the upper limit of the H1 model.  
H1 model:  
LL = 0  
UL = low load  
In the table, LL and UL refer to the 95% CIs of the means (and not to the LL and UL of the H1 models).
```{r big data hiMlo, echo = rout}
DBF10 = numeric()

# create matrix with measure, study, n, mean no load, 
# diff hiMlo, LL 95%CI, UL 95%CI, BF10 hiMlo, BF01 hiMlo,
LL = 0

# amp
# study 1
UL = mean(Dtmp1$AmpSmNlo)
tmp = Dtmp1$AmpSmNlo-Dtmp1$AmpSmNhi
DBF10 = rbind(DBF10, c('Study IV s1','Amp', nrow(Dtmp1), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# study 2
UL = mean(Dtmp2$AmpSmNlo)
tmp = Dtmp2$AmpSmNlo-Dtmp2$AmpSmNhi
DBF10 = rbind(DBF10, c('Study IV s2','Amp', nrow(Dtmp2), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# ASSR2
UL = mean(Dtmp3$AmpSmNlo)
tmp = Dtmp3$AmpSmNlo-Dtmp3$AmpSmNhi
DBF10 = rbind(DBF10, c('Study V', 'Amp', nrow(Dtmp3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(Dall$AmpSmNlo)
tmp = Dall$AmpSmNlo-Dall$AmpSmNhi
DBF10 = rbind(DBF10, c('Combined','Amp', nrow(Dall), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# itc
# study 1
UL = mean(Dtmp1$ItcSmNlo)
tmp = Dtmp1$ItcSmNlo-Dtmp1$ItcSmNhi
DBF10 = rbind(DBF10, c('Study IV s1','Itc', nrow(Dtmp1), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# study 2
UL = mean(Dtmp2$ItcSmNlo)
tmp = Dtmp2$ItcSmNlo-Dtmp2$ItcSmNhi
DBF10 = rbind(DBF10, c('Study IV s2','Itc', nrow(Dtmp2), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# ASSR2
UL = mean(Dtmp3$ItcSmNlo)
tmp = Dtmp3$ItcSmNhi-Dtmp3$ItcSmNlo
DBF10 = rbind(DBF10, c('Study V', 'Itc', nrow(Dtmp3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(Dall$ItcSmNlo)
tmp = Dall$ItcSmNlo-Dall$ItcSmNhi
DBF10 = rbind(DBF10, c('Combined', 'Itc', nrow(Dall), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))


DBF10 = as.data.frame(DBF10)
colnames(DBF10)=c('Study','Measure','N','Mlo',
                  'M-loMhi','LL-loMhi','UL-loMhi','BF10-loMhi','BF01-loMhi')

# convert character to numeric
i = 3:9
DBF10[, i] = apply(DBF10[,i],2, function(x) as.numeric(as.character(x)))
DBF10 %>%
  kable(digits = 3,
        col.names = c('Study','Measure','N','Mean',
                      'Mean','LL', 'UL', 'BF10', 'BF01')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = 'left') %>%
  add_header_above(c(" " = 3, "low" = 1, "low minus high" = 5)) %>%
  row_spec(c(4,8), bold = T)
```

### task effect: no minus low
Low load is used as the upper limit of the H1 model.  
H1 model:  
LL = 0  
UL = no load  

Note that Study IV s1 is excluded because no load was not administered. 

In the table, LL and UL refer to the 95% CIs of the means (and not to the LL and UL of the H1 models).  
```{r big data loMno, echo = rout}
# compare low with no load
DBF10 = numeric()

# create matrix with measure, study, n, mean low load, 
# diff loMhi, LL 95%CI, UL 95%CI, BF01 loMhi
LL = 0

# amp
# study 2
UL = mean(Dtmp2$AmpSmNno)
tmp = Dtmp2$AmpSmNno-Dtmp2$AmpSmNlo
DBF10 = rbind(DBF10, c('Study IV s2','Amp', nrow(Dtmp2), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# ASSR2
UL = mean(Dtmp3$AmpSmNno)
tmp = Dtmp3$AmpSmNno-Dtmp3$AmpSmNlo
DBF10 = rbind(DBF10, c('Study V', 'Amp', nrow(Dtmp3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(D2and3$AmpSmNno)
tmp = D2and3$AmpSmNno-D2and3$AmpSmNlo
DBF10 = rbind(DBF10, c('Combined','Amp', nrow(D2and3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# itc
# study 2
UL = mean(Dtmp2$ItcSmNno)
tmp = Dtmp2$ItcSmNno-Dtmp2$ItcSmNlo
DBF10 = rbind(DBF10, c('Study IV s2','Itc', nrow(Dtmp2), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# ASSR2
UL = mean(Dtmp3$ItcSmNno)
tmp = Dtmp3$ItcSmNno-Dtmp3$ItcSmNlo
DBF10 = rbind(DBF10, c('Study V', 'Itc', nrow(Dtmp3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(D2and3$ItcSmNno)
tmp = D2and3$ItcSmNno-D2and3$ItcSmNlo
DBF10 = rbind(DBF10, c('Combined', 'Itc', nrow(D2and3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))


DBF10 = as.data.frame(DBF10)
colnames(DBF10)=c('Study','Measure','N','Mno',
                  'M-noMlo','LL-noMlo','UL-noMlo','BF10-noMlo','BF01-noMlo')

# convert character to numeric
i = 3:9
DBF10[, i] = apply(DBF10[,i],2, function(x) as.numeric(as.character(x)))
DBF10 %>%
  kable(digits = 3,
        col.names = c('Study','Measure','N','Mean',
                      'Mean','LL', 'UL', 'BF10', 'BF01')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = 'left') %>%
  add_header_above(c(" " = 3, "no" = 1, "no minus low" = 5)) %>%
  row_spec(c(3,6), bold = T)
```


### combined effect: no minus high
High load is used as the upper limit of the H1 model.  
H1 model:  
LL = 0  
UL = no load  

Note that Study IV s1 is excluded because no load was not administered.  

In the table, LL and UL refer to the 95% CIs of the means (and not to the LL and UL of the H1 models).
```{r big data hiMno, echo = rout}

Dall = merge(Dtmp1, Dtmp2, all = T)
Dall = merge(Dall, Dtmp3, all = T)

D2and3 = merge(Dtmp2, Dtmp3, all = T)


DBF10 = numeric()

# create matrix with measure, study, n, mean no load, 
# diff hiMno, LL 95%CI, UL 95%CI, BF10 hiMno, BF01 hiMno,
# diff hiMlo, LL 95%CI, UL 95%CI, BF10 hiMlo, BF01 hiMlo,
LL = 0

# amp
# study 2
UL = mean(Dtmp2$AmpSmNno)
tmp = Dtmp2$AmpSmNno-Dtmp2$AmpSmNhi
DBF10 = rbind(DBF10, c('Study IV s2','Amp', nrow(Dtmp2), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# ASSR2
UL = mean(Dtmp3$AmpSmNno)
tmp = Dtmp3$AmpSmNno-Dtmp3$AmpSmNhi
DBF10 = rbind(DBF10, c('Study V', 'Amp', nrow(Dtmp3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(D2and3$AmpSmNno)
tmp = D2and3$AmpSmNno-D2and3$AmpSmNhi
DBF10 = rbind(DBF10, c('Combined','Amp', nrow(D2and3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# itc
# study 2
UL = mean(Dtmp2$ItcSmNno)
tmp = Dtmp2$ItcSmNno-Dtmp2$ItcSmNhi
DBF10 = rbind(DBF10, c('Study IV s2','Itc', nrow(Dtmp2), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# ASSR2
UL = mean(Dtmp3$ItcSmNno)
tmp = Dtmp3$ItcSmNno-Dtmp3$ItcSmNhi
DBF10 = rbind(DBF10, c('Study V', 'Itc', nrow(Dtmp3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))

# combined
UL = mean(D2and3$ItcSmNno)
tmp = D2and3$ItcSmNno-D2and3$ItcSmNhi
DBF10 = rbind(DBF10, c('Combined', 'Itc', nrow(D2and3), UL, 
                       mean(tmp), ci(tmp), 1/BFfitH1(LL = 0, UL, tmp), BFfitH1(LL = 0, UL, tmp)))


DBF10 = as.data.frame(DBF10)
colnames(DBF10)=c('Study','Measure','N','Mno',
                  'M-noMhi','LL-noMhi','UL-noMhi','BF10-noMhi','BF01-noMhi')

# convert character to numeric
i = 3:9
DBF10[, i] = apply(DBF10[,i],2, function(x) as.numeric(as.character(x)))
DBF10 %>%
  kable(digits = 3,
        col.names = c('Study','Measure','N','Mean',
                      'Mean','LL', 'UL', 'BF10', 'BF01')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = 'left') %>%
  add_header_above(c(" " = 3, "no" = 1, "no minus high" = 5)) %>%
  row_spec(c(3,6), bold = T)
```
